\bf Visual Inference for Significance and Goodness-of-Fit Testing for a Social Network Model

### 2017-10-28 ASApaper/paper-child.Rnw
add pdf
finish section exper setup for sig testing

We use the estimates given in Table~\ref{tab:fittedvalues} to simulate from models M1 through M6. We discuss the simulation procedure and how we use the simulations in Section~\ref{sec:expersetup}.

@@

To construct a lineup, we simulate five networks from the null model and one network from the alternative model. We chose to expose our participants to only six plots at a time in order to show the node-link diagrams in more detail and to lower their cognitive load. Typically, lineup experiments are done with sets of 20 plots at a time c.f.~\citet{loy:2015, vanderplas:2016}, but we determined that not enough structure could be shown in each plot for 20 node-link diagrams. An example of a lineup like those shown to our participants is shown on the right side of the image  in Figure~\ref{fig:shiny}.  In this lineup, model M4 is the alternative model, and model M1 is the null model. To simulate lineups from the models, we set the parameters to the values given in Table~\ref{tab:fitted values} for all parameters within the respective models, with the exception of $\beta_5$. For $\beta_5$, twice the estimated value was used. More detail on why we use twice the fitted value is provided in Section~\ref{sec:setupvd}.\footnote{If you would like to explore the kinds of lineups we use in further detail, please visit \url{https://sctyner.shinyapps.io/saom_lineup_creation/}}. To get the simulations, we used the \tettt{siena07} function in \texttt{RSiena} \citep{RSiena}.

@@

We want to explore the role of each of these parameters in the objective functions for each model.

@@

@@

\section{Experiment Results}

>>>>

We want to explore the role of each of these parameters in the objective functions for each model. So, we use the estimates given in Table~\ref{tab:fittedvalues} to simulate from models M1 through M6. We discuss the simulation procedure and how we use the simulations in Section~\ref{sec:expersetup}.

@@

To construct a lineup, we simulate five networks from the null model and one network from the alternative model. We chose to expose our participants to only six plots at a time in order to show the node-link diagrams in more detail and to lower their cognitive load. Typically, lineup experiments are done with sets of 20 plots at a time c.f.~\citet{loy:2015, vanderplas:2016}, but we determined that not enough structure could be shown in each plot for 20 node-link diagrams. An example of a lineup like those shown to our participants is shown on the right side of the image  in Figure~\ref{fig:shiny}.  In this lineup, model M4 is the alternative model, and model M1 is the null model. To simulate lineups from the models, we set the parameters to the values given in Table~\ref{tab:fitted values} for all parameters within the respective models, with the exception of $\beta_5$. For $\beta_5$, twice the estimated value was used. More detail on why we use twice the fitted value is provided in Section~\ref{sec:setupvd}.\footnote{If you would like to explore the kinds of lineups we use in further detail, please visit \url{https://sctyner.shinyapps.io/saom_lineup_creation/}}. To get the simulations, we used the \texttt{siena07} function in \texttt{RSiena} \citep{RSiena}.

@@

To explore stochastic actor-oriented models through visual inference, we show a series of lineups to independent observers recruited through Amazon Mechanical Turk. We provide more details on the Turk setup in Section~\ref{sec:res}.

@@

In the significance testing protocol, a parameter of interest is selected to test, say $\beta_k$. The hypotheses we use to generate lineups are:

\begin{description}
\item $H_0$: $\beta_k = 0 $
\item $H_A$: $\beta_k \neq $
\end{description}

Under the null hypothesis, we assume that the model that generated the network data is the simplest model presented in Section~\ref{sec:models}, model M1. Thus, the five null plots in the lineup are simulations from M1 with $\beta_1, \beta_2$ set to the estimates given in Table~\ref{tab:fittedvalues} for M1. The alternate model is the model with $\beta_1, \beta_2$, and $\beta_k$ in the objective function, with the remaining plot simulated from the appropriate model.

The lineup generated under this scenario is shown to independent viewers. If the viewers pick out the alternative data plot, that is evidence in favor of the null hypothesis, while picking one of the null plots is evidence against the null hypothesis. The significance tests that we perform in our experiment are for $\beta_3$ and $\beta_4$, making the alternative models M3 and M4, respectively.

@@

\section{Experiment Results}\label{sec:res}
